pirouette: the error BEAST2 makes in inferring a phylogeny

### 2019-02-28 article.tex
Re-create figure 1, fix https://github.com/richelbilderbeek/pirouette_article/issues/10

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    pirouette pipeline
  }
  \label{fig:pipeline}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{workflow.png}
  \caption{
    \texttt{pirouette} pipeline. 
    The pipeline starts from a true phylogeny (1a), 
    that is converted to an alignment (2a), which is used
    to create a BEAST2 posterior of phylogenies (3a),
    which is compared to the true phylogeny (1a) using
    the nLTT statistic (4a), resulting in an error distribution (5a).
    Optionally, a twin phylogeny (1b) can be generated from a true
    phylogeny (1a), which then results in an error distribution (5b) with
    the similar intermediate steps 
  }
  \label{fig:pipeline}
\end{figure}
